---
title: "Wine Regression"
author: "Joseph Oliveira"
date: "7/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(xgboost)
library(tidyverse)
library(tree)
library(leaps)
set.seed(5)
```

```{r}
wine_train <- read_csv('../Data/Clean/wine_train.csv') %>%
  rename('fixed_acidity' = `fixed acidity`,
         'vol_acidity' = `volatile acidity`,
         'citric_acid' = `citric acid`,
         'resid_sugar' = `residual sugar`,
         'free_SO2' = `free sulfur dioxide`,
         'tot_SO2' = `total sulfur dioxide`)
wine_test <- read_csv('../Data/Clean/wine_test.csv') %>%
  rename('fixed_acidity' = `fixed acidity`,
         'vol_acidity' = `volatile acidity`,
         'citric_acid' = `citric acid`,
         'resid_sugar' = `residual sugar`,
         'free_SO2' = `free sulfur dioxide`,
         'tot_SO2' = `total sulfur dioxide`)
```

#### tree model approach

```{r}
wine_tree_reg <- tree(quality  ~ ., data = wine_train)
wine_tree_cv <- cv.tree(wine_tree_reg, FUN = prune.tree)

plot(wine_tree_cv$size, wine_tree_cv$dev, type = 'b')
```

Going with a depth of 5 max for a boosted tree approach. 

```{r}
wine_train_mat <- wine_train %>%
  select(-quality) %>%
  as.matrix()

wine_test_mat <- wine_test %>%
  select(-quality) %>%
  as.matrix()

wine_tree_bst <- xgboost(data = wine_train_mat,
                                label = wine_train$quality,
                                max.depth = 5,
                                eta = 0.1,
                                nrounds = 100,
                                objective = "reg:squarederror")
```

```{r}
pred_bst <- predict(wine_tree_bst, wine_test_mat)

mse_bst <- mean((pred_bst - wine_test$quality)^2)
misclas_bst <- 1 - mean(round(pred_bst) == wine_test$quality)
```

Boosted model test MSE: `r mse_bst`
Rounding the predicted scores, the boosted misclassification rate: `r misclas_bst`

#### linear regression

```{r}
wine_lm <- lm(quality ~ ., data = wine_train)
pred_lm <- predict(wine_lm, select(wine_test, -quality))
mse_lm  <- mean((pred_lm - wine_test$quality)^2)
misclas_lm <- 1 - mean(round(pred_lm) == wine_test$quality)
```

LM model test MSE: `r mse_lm`
Rounding the predicted scores, the linear model misclassification rate: `r misclas_lm`

```{r}
wine_lm_full <- regsubsets(quality ~ ., data = wine_train, nvmax = 10)
summary(wine_lm_full)
```

Among the variables, `alcohol`, `vol_acidity`, `sulphates`, `total sulphur dioxide`, and `chlorides` are the top predictors in the selection process.

```{r}
wine_lm_fwd <- regsubsets(quality ~ ., data = wine_train, nvmax = 5, method = "forward")
summary(wine_lm_fwd)
```

The same 5 variables are selected in forward selection and backward selection. 

```{r}
wine_lm_bwd <- regsubsets(quality ~ ., data = wine_train, nvmax = 5, method = "backward")
summary(wine_lm_bwd)
```

```{r}
wine_lm_five <- lm(quality ~ alcohol + vol_acidity + 
                sulphates + tot_SO2 + chlorides, data = wine_train)
pred_lm_five <- predict(wine_lm_five, select(wine_test, -quality))
mse_lm_five  <- mean((pred_lm_five - wine_test$quality)^2)
misclas_lm_five <- 1 - mean(round(pred_lm_five) == wine_test$quality)
```

Boosted model test MSE: `r mse_lm_five`
Rounding the predicted scores, the boosted misclassification rate: `r misclas_lm_five`

```{r}

```

